\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{lmodern}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
    \textbf{\Huge \scshape Ashish Prasad} \\ \vspace{10pt}
    \small \href{mailto:ashishprasad949@gmail.com}{ashishprasad949@gmail.com} $|$ 
    Jamshedpur, Jharkhand, India $|$
    \href{https://github.com/ashudevcodes}{github.com/ashudevcodes} $|$
    \href{https://linkedin.com/in/ashudevcodes}{linkedin.com/in/ashudevcodes}
\end{center}

\section{Professional Summary}
\resumeItemListStart
    \resumeItem{Backend/Full Stack Developer with 1+ years of experience designing and deploying scalable web applications and RESTful APIs. Proficient in JavaScript, Python, Java, and cloud technologies (AWS, Docker). Demonstrated impact in logistics tech and open source. Strong problem-solving, collaboration, and communication skills.}
\resumeItemListEnd

\section{Technical Skills}
\resumeItemListStart
    \resumeItem{\textbf{Languages:} JavaScript (Node.js, TypeScript), Python, Java, C++, Go, Lua}
    \resumeItem{\textbf{Web/Frameworks:} Node.js, Express.js, React, Spring Boot, Django, REST APIs, WebSocket, HTTP, TCP/UDP}
    \resumeItem{\textbf{Cloud/DevOps:} AWS (EC2, S3, Lambda), Docker, CI/CD (GitHub Actions), Linux}
    \resumeItem{\textbf{Databases:} MongoDB, PostgreSQL, MySQL}
    \resumeItem{\textbf{Tools:} Git, Vim, Jira, Postman}
\resumeItemListEnd

\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {GoTrans Logistics}{Kolkata, West Bengal -- Remote}
    {Backend Developer}{May 2024 -- Mar 2025}
    \resumeItemListStart
        \resumeItem{Developed and maintained RESTful APIs (Node.js, Express.js) handling 1,000+ daily requests with 99.9\% uptime.}
        \resumeItem{Designed and implemented JWT-based authentication for 500+ active users, achieving zero security breaches.}
        \resumeItem{Deployed microservices on AWS using Docker, reducing deployment time by 30\%.}
        \resumeItem{Collaborated with cross-functional teams to deliver features on schedule and improve code quality through code reviews.}
    \resumeItemListEnd

\resumeSubheading
    {Open Source Contributor}{}
    {GitHub}{Jan 2023 -- Present}
    \resumeItemListStart
        \resumeItem{Resolved bugs and enhanced features in a movie streaming app, improving user experience for 1,000+ users.}
        \resumeItem{Contributed 20+ pull requests with 95\% acceptance rate across multiple open-source projects.}
        \resumeItem{Collaborated with global teams, following best practices in code review and version control.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
    {\textbf{Anonymous Writing Blog Web App}}
    {$|$ \emph{\href{https://github.com/ashudevcodes/Blog-application}{Code}} $|$ \emph{\href{http://blog-application-sand-nu.vercel.app}{Live}} $|$}
    \resumeItemListStart
        \resumeItem{Built a full-stack blogging platform (React, TypeScript, Node.js, MongoDB, Express.js).}
        \resumeItem{Implemented automated content filtering using NLP for a safe community.}
        \resumeItem{Designed intuitive UI/UX for seamless blog management and photo sharing.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Google Map Lite}}
    {$|$ \emph{\href{https://github.com/ashudevcodes/web-selfie-app}{Code}} $|$ \emph{\href{http://dataselfieapp.vercel.app}{Live}} $|$}
    \resumeItemListStart
        \resumeItem{Developed a mini map app showing user and ISS locations with 99\% accuracy.}
        \resumeItem{Integrated OpenStreet Map and ISS API for real-time location visualization.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Steam Game Recommendation System}}
    {$|$ \emph{\href{https://github.com/ashudevcodes/Steam-Game-Recommendation-System}{Code}} $|$ \emph{\href{https://huggingface.co/spaces/ashudevcodes/Steam-game-Recommendation-System}{Live}} $|$}
    \resumeItemListStart
        \resumeItem{Engineered a personalized recommendation engine using machine learning and NLP.}
        \resumeItem{Processed 1,800+ game records to provide accurate, user-tailored suggestions.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{MongoDB-Talker}}
    {$|$ \emph{\href{https://github.com/ashudevcodes/Talk-to-MongoDB-Database}{Code}} $|$}
    \resumeItemListStart
        \resumeItem{Built secure user authentication with MongoDB, Bcrypt, and JWT.}
        \resumeItem{Ensured robust password hashing and stateless API security.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {Arka Jain University}{Mohanpur, Jharkhand}
    {Bachelor of Computer Applications}{Oct 2022 -- Apr 2024}
    \resumeItemListStart
        \resumeItem{Coursework: Data Structures \& Algorithms, OOP, DBMS, AI, Software Development}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
